---
output: github_document
---

# vaccc19de

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/friep/vaccc19de/workflows/R-CMD-check/badge.svg)](https://github.com/friep/vaccc19de/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/vaccc19de)](https://CRAN.R-project.org/package=vaccc19de)
<!-- badges: end -->

The goal of vaccc19de (**vacc**inations **c**ovid **19** **de**utschland) is to provide functions to easily get and extract data on the progress of vaccinations in German Bundesländer that is provided daily by the Robert-Koch-Institut (RKI) on [this page](https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Daten/Impfquotenmonitoring.html). The package is used to automatically collect data in the accompanying [vaccc19de_rki_data repository](https://github.com/friep/vaccc19de_rki_data).

The package is used in the [vaccc19de_dashboard](https://github.com/favstats/vaccc19de_dashboard) repository where you can also find the current version of the following two datasets:

- [cumulative data](https://github.com/favstats/vaccc19de_dashboard/blob/main/data/cumulative_time_series.csv)
- ["decumulated" data of daily differences](https://github.com/favstats/vaccc19de_dashboard/blob/main/data/diffs_time_series.csv)

Please refer to the README of the [vaccc19de_dashboard](https://github.com/favstats/vaccc19de_dashboard) for more information on the data. 


## Installation

vaccc19de is not on CRAN. You can install the development version from GitHub with:

``` r
remotes::install_github("friep/vaccc19de")
```


## Usage

Download the currently available data from the RKI:

```{r}
library(vaccc19de)
path <- rki_download_xlsx() # returns path to xlsx invisibly
# rki_extract_sheet_csvs(path) # optional to store the raw sheets as csvs
cumulative <- rki_extract_cumulative_data(path)
```

Or download the full time series from [GitHub](https://github.com/favstats/vaccc19de_dashboard/tree/main/data):

```{r, eval=FALSE}
cumulative_ts <- rki_download_cumulative_ts()
cumulative_ts
```

"decumulate" it / create the time series of differences:
```{r}
diffs_ts <- rki_extract_diffs(cumulative_ts)
diffs_ts
```

Finally, you can also download the "decumulated" data directly from [GitHub](https://github.com/favstats/vaccc19de_dashboard/tree/main/data):

```{r, eval=FALSE}
cumulative_ts <- rki_download_diffs_ts()
```


## Roadmap
- function to "longify" the data by indication
- more robust data cleaning

## Contribute
Before filing an issue, please check the list of issues. When forking, please create your PR against the `dev` branch. 

## Licensing information

Data in folder `tests/testthat/test_data` was downloaded from the Robert Koch Institut's website on 2020-12-30: https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Daten/Impfquotenmonitoring.html 
